\documentclass[12pt]{article}

\usepackage{cwpuzzle}

\pagestyle{empty}

\begin{document}

\begin{center}
{\large \textbf{1. Farm Equipment for the 21$^{st}$ Century}} \medskip

{\small by Brent Yorgey \\
  6/26/04}
\end{center}
\medskip



\begin{Puzzle}{10}{10}
  |[1]A  |[2]I  |[3]L  |[4]S  |*     |[5]C  |[6]O  |[7]N  |[8]C  |[9]H  |.
  |[10]S |C     |O     |T     |*     |[11]A |D     |I     |E     |U     |.
  |[12]S |U     |P     |E     |[13]R |S     |E     |E     |D     |S     |.
  |*     |*     |*     |[14]A |R     |K     |*     |[15]C |A     |T     |.
  |[16]I |[17]T |[18]E |M     |S     |*     |[19]P |E     |R     |L     |.
  |[20]M |I     |R     |Y     |*     |[21]P |O     |S     |S     |E     |.
  |[22]A |P     |A     |*     |[23]C |T     |N     |*     |*     |*     |.
  |[24]G |P     |S     |[25]T |R     |A     |C     |[26]T |[27]O |[28]R |.
  |[29]E |L     |E     |G     |Y     |*     |[30]H |I     |F     |I     |.
  |[31]S |E     |R     |I     |O     |*     |[32]O |N     |T     |O     |.
\end{Puzzle}

\begin{PuzzleClues}{\textbf{Across}}\bigskip \\
  \Clue{1}{AILS}{Doesn't feel well} \\
  \Clue{5}{CONCH}{Lord of the Flies token} \\
  \Clue{10}{SCOT}{$\underline{\phantom{SCOT}}$-free} \\
  \Clue{11}{ADIEU}{Parisian farewell} \\
  \Clue{12}{SUPERSEEDS}{Genetically modified plants that replace others?} \\
  \Clue{14}{ARK}{Covenant holder} \\
  \Clue{15}{CAT}{Jazz musician} \\
  \Clue{16}{ITEMS}{Entities} \\
  \Clue{19}{PERL}{Script language} \\
  \Clue{20}{MIRY}{Good for getting stuck} \\
  \Clue{21}{POSSE}{Sheriff's men} \\
  \Clue{22}{APA}{Shrink org.} \\
  \Clue{23}{CTN}{Reciprocal of tangent: alt.} \\
  \Clue{24}{GPSTRACTOR}{Farm vehicle that never gets lost?} \\
  \Clue{29}{ELEGY}{Poetic lament} \\
  \Clue{30}{HIFI}{Quality sound: abbr.} \\
  \Clue{31}{SERIO}{Comic introduction} \\
  \Clue{32}{ONTO}{Aware of}
\end{PuzzleClues}
\begin{PuzzleClues}{\textbf{Down}}\bigskip \\
  \Clue{1}{ASS}{Fool} \\
  \Clue{2}{ICU}{Hospital loc.} \\
  \Clue{3}{LOP}{Trim} \\
  \Clue{4}{STEAMY}{Explicit} \\
  \Clue{5}{CASK}{It's made of staves} \\
  \Clue{6}{ODE}{Celebratory verse} \\
  \Clue{7}{NIECES}{Female relatives} \\
  \Clue{8}{CEDARS}{Lebanese plants?} \\
  \Clue{9}{HUSTLE}{Move quickly} \\
  \Clue{13}{RRS}{Transp. lines} \\
  \Clue{16}{IMAGES}{Likenesses} \\
  \Clue{17}{TIPPLE}{Drink habitually} \\
  \Clue{18}{ERASER}{Lead insurance policy?} \\
  \Clue{19}{PONCHO}{Coat of polyurethane, perhaps?} \\
  \Clue{21}{PTA}{Home-school org.?} \\
  \Clue{23}{CRYO}{Freezing: pref.} \\
  \Clue{25}{TGI}{$\underline{\phantom{TGI}}$ Friday's} \\
  \Clue{26}{TIN}{Cookie container} \\
  \Clue{27}{OFT}{Poetic frequency} \\
  \Clue{28}{RIO}{River, to Rivera}
\end{PuzzleClues}

\end{document}